Replication Code

### 2020-05-08 replication_code.Rmd
reformatted

stargazer(
  shp_2,
  type = "latex",
  out="./replication-table-2.tex",
  header = FALSE,
  summary = FALSE,
  font.size = "small",
  column.sep.width = "-7.5pt",
  title = "Measures across panel waves in the SHP and the LISS"
)
```

>>>>

stargazer(
  shp_2,
  type = "latex",
  out="./replication-table-2.tex",
  header = FALSE,
  summary = FALSE,
  font.size = "tiny", 
  column.sep.width = "-7.5pt",
  title = "Measures across panel waves in the SHP and the LISS",
  notes = "\\parbox[t]{15cm}{The above table indicates the years in which data was present for each question on the two surveys. The lines represent years for which we have data. }"
)
```
